Implementing a Capability Machine model into Iris

### 2020-01-01 prisc-2020-talk/slides.tex
added slides about challenges

\textbf{Iris:} Higher-order Concurrent Separation Logic Framework
\begin{itemize}
	\item<2-> Foundational
	\item<3-> Implemented in Coq -- equipped with an interactive proof mode
	\item<4-> Framework -- embed any language and its operational semantics into Iris
	\item<5-> Comes equipped with: 
		\begin{itemize}
			\item<5-> Invariants
			\item<6-> Ghost state
		\end{itemize}
\end{itemize}

\uncover<5->{We can take advantage of Iris' step-indexed model and invariants to mechanize step-indexed Kripke logical relations with recursive worlds in a succinct and elegant way.}

>>>>

\textbf{Iris:} Higher-order Concurrent Separation Logic Framework
\begin{itemize}
	\item<2-> Foundational
	\item<3-> Implemented in Coq -- equipped with an interactive proof mode
	\item<4-> Framework -- embed any language and its operational semantics into Iris
	\item<5-> Comes equipped with: 
		\begin{itemize}
			\item<5-> Invariants
			\item<6-> Ghost state
			\item<7-> Always and Later Modalities
		\end{itemize}
\end{itemize}

\uncover<8->{We can take advantage of Iris' step-indexed model and invariants to mechanize step-indexed Kripke logical relations with recursive worlds in a succinct and elegant way.}

\begin{frame}
\frametitle{Expressing Capability Safety in Iris - Challenges}

\begin{itemize}
	\item Region invariants: Iris invariants
	\item Future world relation: frame preserving updates and world satisfaction 
	\item Step indexing: later modality
\end{itemize}

\textbf{Challenges}
\begin{itemize}
	\item<2-> Iris was designed with more high level languages in mind, how do we embed a low level machine language into Iris
	\item<3-> Iris abstracts away certain details we want to reason about directly
	\item<4-> There is only one frame preserving update, we need to distinguish between two future world relations
\end{itemize}
